\begin{frame}[allowframebreaks]{Functional requirements}

\begin{enumerate}
	\item The service shall accept only valid input: \begin{enumerate}
		\item The service shall assure that each provided address exists.
		\item The service can accept only requests with full personal data of the customer (name, surname and phone number).
	\end{enumerate}
	
	\item The service shall guarantee the non-ubiquity of the actors: \begin{enumerate}
		\item A taxi driver must be registered once.		\item A registered customer can be registered only once.		\item A taxi shall be registered only once.		\item A taxi must have one and only one taxi driver, a taxi driver must have one and only one taxi.
	\end{enumerate}
	
	\item The system has to ensure the security in the login process: \begin{enumerate}
		\item Only registered customer can login in myTaxiApp.
		\item Only verified taxi driver can login in myTaxiAssist.
	\end{enumerate}
	
	\item The service shall provide a method to verify the driver: \begin{enumerate}
		\item Only authorised personnel can add or remove a taxi driver and/or a taxi.
	\end{enumerate}
	
	\item The service shall accept only valid reservations: \begin{enumerate}
		\item The service shall allow only registered customers to reserve a taxi.
		\item The system shall accept reservations only if they are made between 24 hours and 2 hours before the request time.
	\end{enumerate}
	
	\item The service shall guarantee a correct taxi allocation: \begin{enumerate}
		\item One taxi cab every four passengers must be allocated by the system.
		\item The service must ensure that a taxi is allocated to only one request at the same time.
		\item A non available taxi cab shall not be allocated to a request.
		\item The service has to provide a taxi to a customer within 10 mins.
		\item The service has to guarantee a fair management of the taxi queue.
		\item When a taxi driver refuses a request, the system must push the taxi at the end of the queue.
		\item While a taxi has a customer on board, it cannot be allocated.
		\item If a request has been accepted by the system, the customer must be taken to its destination: \begin{enumerate}
			\item If the taxi driver refuses the request, the request is forwarded to the first taxi in the queue.
			\item If no taxis are available in the area, the first taxi in the queue of adjacent areas must be selected.
			\item If the taxi breaks down, another taxi has to be allocated.
		\end{enumerate}
	\end{enumerate} 
\end{enumerate}
\end{frame}
